---
title: "4. Input/Output"
output: 
  html_notebook: 
    toc: yes
    toc_depth: 4
---

### 4.1 R Output

The **print()** is a function that outputs to your console window whatever you say you want to print out.

It prints the specified output to the screen or other standard output device. The output can be a string, or any other object, the object will be converted into a string before written to the screen.

```{r}
print("Welcome to INSAID")
```

### 4.2 R Input

In R, there are a series of functions that can be used to request an input from the user.

#### 4.2.1 Reading from the keyboard

To read from the keyboard you can use **'scan()'** function. Read data values into a vector or list from the console.

```{r}
x = scan()
```

___

We can use **readline()** for inputing a line from the keyboard in the form of a string

```{r}
y = readline()
```

#### 4.2.2 Take input from user

Lets take an example where we can see both input and output functions of R:

```{r}
name = readline(prompt="Enter name: ")
age = readline(prompt="Enter age: ")
# convert character into integer
age = as.integer(age)
print(paste("Hey,", name, "next year you will be", age+1, "years old."))
```

