---
title: "Assignment"
output: html_notebook
---

**1. Use various utility functions discussed to create vectors containing these values. You need to create both (first containing 10 values and another containing 26) vectors separately.**

```{r}
## [1] 2 4 8 16 32 64 128 256 512 1024

## [1] "a26" "b25" "c24" "d23" "e22" "f21" "g20" "h19" "i18" "j17" "k16"
## [12] "l15" "m14" "n13" "o12" "p11" "q10" "r9" "s8" "t7" "u6" "v5"
## [23] "w4" "x3" "y2" "z1"
```

___

**2. Below given is a vector containing first lines of many addresses. Extract city names from all the addresses using string functions. Hint: you can use a for loop to iterate over results of strsplit for further processing.**

```{r}
address_list = c("802/hiranandani/Mumbai",
               "2A/kalka-Delhi",
               "345#near adyar#Chennai",
               "10-shyaam bazzar-Kolkata")
```

___

Result will be as follows:

```{r}
## [1] "Mumbai"
## [1] "Delhi"
## [1] "Chennai"
## [1] "Kolkata"
```

___

**3. Use following bit to create a vector with prime numbers in 1:47. (Prime numbers are numbers which are divisible only by themselves)**

```{r}
primes = c(2,3,5,7,11,13,17,19,23,29,31,37,41,43,47)
```

___

Any number from 48 to 100 which is not divisible by any of the above listed primes is also a prime. Print
those prime numbers from 48 to 100.

Result will be as follows:

```{r}
## [1] 53
## [1] 59
## [1] 61
## [1] 67
## [1] 71
## [1] 73
## [1] 79
## [1] 83
## [1] 89
## [1] 97
```

___

**4. Find out, how many cars are there are in the dataset mtcars which have automatic transmission, number of forward gears higher than 3 and below average mileage. List their names. Calculate average mileage from the data itself. To find out which variable in the data represent mentioned above information do ?mtcars**

___

**5. There is no native function in R to calculate mode for a variable. The function "mode" returns storage mode of an object, not the statistical mode that we discussed in the class. Write a function which returns modes of a character vector. Test that on the following vectors.**

```{r}
set.seed(2)
x=sample(letters[1:5],50,replace=T)
y=sample(letters[1:3],50,replace=T)
```

___

Result will be as following:

```{r}
## [1] "e"
## [1] "a"
```


